Searching for Software in NSF Awards

### 2023-02-14 paper/paper.qmd
Minor styling adjustments to paper

## Citation Style Language
# See https://github.com/citation-style-language/styles for more options
# We default to PNAS (Proceedings of the National Academy of Sciences)
csl: support/acm-proceedings.csl

@@

  # comment this out to specify detailed document options
  acmart-options: sigconf, review

@@

  keywords:
    - datasets
    - text classification
    - research software
---

@@

Using the compiled NSF-Soft-Search Training dataset, we trained three different models using the text from either the award abstract or project outcomes report. The models trained include a logistic regression model trained with TF-IDF word embeddings (`tfidf-logit`), a logistic regression model trained with semantic embeddings (`semantic-logit`), and a fine-tuned transformer (`transformer`). The semantic embeddings and the base model from which we fine-tuned our own transformer model was the `distilbert-base-uncased-finetuned-sst-2-english` model [@hf_canonical_model_maintainers_2022]. Each model was trained with 80% of the NSF-Soft-Search Training dataset. We then test each of the models and use F1 to rank each model’s performance.

@@

We wish to thank ....

This work was supported in part by NSF Grant ####

>>>>

## Citation Style Language
# See https://github.com/citation-style-language/styles for more options
# We default to PNAS (Proceedings of the National Academy of Sciences)
# csl: support/acm-proceedings.csl

@@

  # comment this out to specify detailed document options
  acmart-options: sigconf

@@

  keywords:
    - datasets
    - text classification
    - research software

  ccs: |
    \begin{CCSXML}
    <ccs2012>
      <concept>
          <concept_id>10002951.10003227.10003392</concept_id>
          <concept_desc>Information systems~Digital libraries and archives</concept_desc>
          <concept_significance>500</concept_significance>
          </concept>
      <concept>
          <concept_id>10002951.10003317.10003347.10003356</concept_id>
          <concept_desc>Information systems~Clustering and classification</concept_desc>
          <concept_significance>300</concept_significance>
          </concept>
      <concept>
          <concept_id>10011007.10011074</concept_id>
          <concept_desc>Software and its engineering~Software creation and management</concept_desc>
          <concept_significance>300</concept_significance>
          </concept>
      <concept>
          <concept_id>10011007.10011006.10011072</concept_id>
          <concept_desc>Software and its engineering~Software libraries and repositories</concept_desc>
          <concept_significance>100</concept_significance>
          </concept>
    </ccs2012>
    \end{CCSXML}

    \ccsdesc[500]{Information systems~Digital libraries and archives}
    \ccsdesc[300]{Information systems~Clustering and classification}
    \ccsdesc[300]{Software and its engineering~Software creation and management}
    \ccsdesc[100]{Software and its engineering~Software libraries and repositories}
---

@@

Using the compiled NSF-Soft-Search Training dataset, we trained three different models using the text from either the award abstract or project outcomes report. The models trained include a logistic regression model trained with TF-IDF word embeddings (`tfidf-logit`), a logistic regression model trained with semantic embeddings (`semantic-logit`), and a fine-tuned transformer (`transformer`). The semantic embeddings and the base model from which we fine-tuned our own transformer model was the 'distilbert-base-uncased-finetuned-sst-2-english' model [@hf_canonical_model_maintainers_2022]. Each model was trained with 80% of the NSF-Soft-Search Training dataset. We then test each of the models and use F1 to rank each model’s performance.

@@

We thank the USRSSI team, especially Karthik Ram for their input. This material is based upon work supported by the National Science Foundation under Grant 2211275.
